Federated Imputation

### 2020-07-08 synthesizing_partitioned_data.Rmd
Added 10 partitions instead of 5

>>>>

# Ten subsets instead of five

## Uncorrelated predictors

### CART Synthesization

Below, the results are presented when the data is partitioned into 10 subsets, instead of five, corresponding to ten different nodes that are synthesized separately, and then combined into a single dataset that is analysed by means of the standard estimators as presented by @raab_practical_2016. This yields regression coefficients that are equal to
$$
\beta_{M,k} = \sum^M_{m=1} \beta_{m,k} / M,
$$
with a variance of 
$$
V = \bar{v}_M(1+\frac{1}{M}),
$$
where $\bar{v}_M$ equals $\sum^M_{m=1}\frac{v_m}{M}$.

```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
source("2.f Synthesize 10 subsets with and without correlations.R")
```

```{r, echo = F}
bind_rows("n = 100" = p10_summary_out_cart_part_n100, 
          "n = 1000" = p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

### Norm synthesization

```{r, echo = F}
bind_rows("n = 100" = p10_summary_out_norm_part_n100, 
          "n = 1000" = p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

## Correlated predictors

### CART synthesization

```{r, echo = F}
bind_rows("n = 100" = cor_p10_summary_out_cart_part_n100, 
          "n = 1000" = cor_p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

### Norm synthesization

```{r, echo = F}
bind_rows("n = 100" = cor_p10_summary_out_norm_part_n100, 
          "n = 1000" = cor_p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

# Workflow from now on

Necessity to further investigate structure of the data by means of, say, eigenvalues (correlations seem to be okay with large samples, according to results presented)?

## Proposal

@. Verder werken met de completed boys data (ondanks de hoge correlatie sowieso realistischer dan gesimuleerde multivariate normal data). Eventueel zou ik ook nog een andere dataset kunnen zoeken die wellicht meer lijkt op een "standaard" social sciences dataset.
  + Indien we met de boys data werken, kunnen we eventueel ook nog een subset nemen (om te kijken hoe het gaat met "echte" data als we de sample size verkleinen), en we zouden kunnen bootstrappen om een grotere sample te creëren dan de huidige 748 observaties (wellicht met Stef overleggen wat een redelijk aantal observaties en nodes zijn over verschillende ziekenhuizen).
@. Boys dataset bootstrappen, zodat we een "superpopulatie" krijgen. En dan zowel gebootstrapte echte data vergelijken met synthetische versie van elke boodstrap sample. In dat geval dat geval is het gemiddelde over de bootstrap samples de populatie waarde. 
  + 
1. Second point.
